My title

### 2023-03-20 outputs/paper/paper.qmd
modified the setting for plots and tables

```{r}
#| label: fig-billssssss7
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

```

>>>>

```{r}
#| label: fig-billssssss7
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = educ, y = maeduc, color = incom16)) +
  geom_jitter() +
  stat_smooth(method = "lm", se = FALSE) +
  facet_wrap(~incom16)+
  labs(title = "Education vs Mother's Education with respect to Family Income",
       x = "Education (in Years)",
       y = "Mother's Educaion (in Years)",
       fill = "Family Income \n (at Age of 16)")+
  theme_bw()
```
